\documentclass[rnd]{mas_proposal}
% \documentclass[thesis]{mas_proposal}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cedric-Francois},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}


\title{AI Powered Medical diagnosis Assistant }
\author{Bassole Cedric-Francois}
\date{Mars 2022}

% \thirdpartylogo{path/to/your/image}

\begin{document}

\maketitle

\pagestyle{plain}

\section{Problems}
 \textbf{A medical error is a preventable adverse effect of medical care, whether or not it is evident or harmful to the patient.The problems that commonly occur during providing health care are:
}
\begin{itemize}
    \item\textbf{Adverse drug events and improper transfusions } 
    \item\textbf{Misdiagnosis, under and overtreatment}
    \item\textbf{And mistaken patient identities}
\end{itemize}
  
   
   \section{Solution-Project Idea}
   \todo[inline]{\textbf{ This project will mainly articulate on budindg a software to help
   medical staff to improve the care of  patients
   and enhancing safety by using technologie to avoid errors.
   }}
   AI is being used in the medical industries  for layering risk, identifying hotspots in chronic disease, and accounting for the social determinants of health.
  
   \todo[inline]{\textbf{Use accurate machine Machine learning Algorithm to help medical professional to diagnose.
   The main goal srills to help diagnose patients more accurately and also prescribe the most suitable treatment.}}
   
\section{Objectives}

This software will  help medical professional to make decision when diagnoscticing patients.
The software  should be able to:\\
\begin{itemize}
    \item\textbf{\textcolor{violet}{1-Identifie he desease the patient are suffering from}
 (Panic disorder,Metabolic disorder,Eating 
disorder,Asthma,Teething syndrome ect) according to the symptoms discribed by the doctor.} 
\item\textbf{\textcolor{violet}{2-Classifies Benign or Malignant cancer by processing photos of skin lesions.}}

\end{itemize}

\section{Project Approach}

\subsection{Methodologie}
In order to run through this Project, we will grasp together all our knowledge to build and test \textbf{differents machine learning Models},
Inside a \textcolor{blue}{Jupyter Notebook},I will use mainly 3 programming languages : 

\begin{itemize}
    \item \textbf{\textcolor{blue}{Python}}
    \item \textbf{\textcolor{blue}{Julia}}
    \item \textbf{\textcolor{blue}{R}}
\end{itemize}

\subsection{Software interface }

Moreover we will use those \textbf{Frameworks} below to build the FrontEnd and the desktop app.
\begin{itemize}
    \item \textbf{\textcolor{violet}{Visual Studio}}
    \item \textbf{\textcolor{violet}{Flutter SDK and Dart Packages to build the desktop Software} }
    \item \textbf{\textcolor{violet}{ Firebase  API and Node Js }}
\end{itemize}

\subsection{Deployement }
To end up I will Deploy our models on edge devices as embedded models.Indeed the best methods for me is to use a cloud service for continiuous Deployement.
\begin{itemize}
    \item \textbf{\textcolor{purple}{Microsoft Machine Learning Studio or Azure End-point}}
    \item \textbf{\textcolor{purple}{Git CI/CD Worflows}}
    \item  \textbf{\textcolor{purple}{Firebase Hosting services}}
\end{itemize}


\nocite{*}

\end{document}
